---
title: "Base64Encoding"
author: "Anjani Bajaj"
date: "October 30, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Encoding for large ECG dataset

This is the ecg data which is to be encoded in base64. The summary of the data looks like below:

```{r ecg}
ecg <- read.csv("ecg_sample.csv")
ecg$Time <- ecg$Time - min(ecg$Time)              
summary(ecg)
```

# Plots for the raw data

You can also embed plots, for example:

```{r, echo=FALSE}
plot_timespan <- function(t1, t2, ecg_data){
  with(ecg_data[ecg_data$Time >=t1 & ecg_data$Time < t2,],
       plot(ec ~ Time, type='l')
  )
}

plot_timespan(0, 58959, ecg)
```

# Here 7500 stands for 1 minute worth of data (125 * 60 * number of minutes)
```{r}
encodeecg <- data.frame(ecg)
i <- 7500
encodeecg <- encodeecg[1:i,]
ecg_encoded_data <- encodeecg$ec
```
# Trying to use base64 encoding from the library caTools
```
```
```{r}
library(caTools)
encoding1 <- base64encode(ecg_encoded_data, size=NA, endian=.Platform$endian)
nchar(encoding1)
```

# Lossy compression 
Dividing all the mV values by 20 and converting them into integers to accomodate each measurement in 1 byte.
```{r}
encodeecg <- data.frame(ecg)
i <- 7500
encodeecg <- encodeecg[1:i,]
ecg_encoded_data <- encodeecg$ec
lossyecg <- as.integer(ecg_encoded_data/20)
summary(lossyecg)
plot(lossyecg, type= 'l')
```

# Extra Space
Multiplying all the mV values by 20 to accomodate each measurement in ~2 bytes
```{r}
encodeecg <- data.frame(ecg)
i <- 7500
encodeecg <- encodeecg[1:i,]
ecg_encoded_data <- encodeecg$ec
extraspaceecg <- ecg_encoded_data*20
summary(extraspaceecg)
plot(extraspaceecg, type= 'l')
```
